\section{Application Actors}

The Credix application is designed to serve a diverse set of users, each with distinct roles and interactions within the digital meal voucher ecosystem. Understanding these roles is crucial for defining the specific functional and non-functional requirements of the platform.

\begin{itemize}
    \item \textbf{End-User}
    \begin{itemize}
        \item \textbf{Role:} Utilizes the digital meal voucher for payments at participating vendors and manages their personal wallet.
        \item \textbf{Responsibilities:}
        \begin{itemize}
            \item Viewing current digital wallet balance and available credit.
            \item Generating unique, time-bound barcodes for payment.
            \item Reviewing personal transaction history.
            \item Confirming payments via biometric authentication (fingerprint/FaceID).
        \end{itemize}
        \item \textbf{Access:}
        \begin{itemize}
            \item Credix mobile application (Flutter).
            \item Digital wallet interface.
            \item Transaction history and payment generation features.
        \end{itemize}
    \end{itemize}

    \item \textbf{Vendor}
    \begin{itemize}
        \item \textbf{Role:} Accepts Credix payments from end-users via ASM POS terminals and manages their transaction settlements.
        \item \textbf{Responsibilities:}
        \begin{itemize}
            \item Scanning end-user barcodes for payment processing.
            \item Viewing real-time payment confirmations.
            \item Accessing daily/weekly/monthly settlement reports.
            \item Managing their business profile and payment settings.
        \end{itemize}
        \item \textbf{Access:}
        \begin{itemize}
            \item Vendor portal (web-based or integrated with POS).
            \item Transaction processing interface.
            \item Settlement and reporting dashboards.
        \end{itemize}
    \end{itemize}

    \item \textbf{Corporate Client}
    \begin{itemize}
        \item \textbf{Role:} Manages meal credit benefits for their employees, including purchasing, distribution, and policy enforcement.
        \item \textbf{Responsibilities:}
        \begin{itemize}
            \item Bulk purchase of meal credit for their organization.
            \item Allocation and distribution of credit to individual employees or departments.
            \item Setting and adjusting spending limits and expiry dates for employee credits.
            \item Monitoring employee credit usage and generating financial reports.
            \item Managing employee accounts within their corporate structure.
        \end{itemize}
        \item \textbf{Access:}
        \begin{itemize}
            \item Dedicated corporate dashboard.
            \item Credit purchase and distribution module.
            \item Employee management and policy configuration tools.
            \item Usage reports and analytics.
        \end{itemize}
    \end{itemize}

    \item \textbf{Administrator}
    \begin{itemize}
        \item \textbf{Role:} Oversees and configures the entire Credix platform, ensuring its smooth operation and security.
        \item \textbf{Responsibilities:}
        \begin{itemize}
            \item Creation, modification, and logical deletion of user accounts (End-Users, Vendors, Corporates).
            \item Assignment and revocation of roles (e.g., activating/deactivating corporate accounts, managing vendor access).
            \item Monitoring system activity, including fraud detection and transaction anomalies.
            \item Managing system configurations (e.g., payment thresholds for OTP, credit expiry rules).
            \item Resolving disputes and handling support requests.
        \end{itemize}
        \item \textbf{Access:}
        \begin{itemize}
            \item Comprehensive administrative dashboard.
            \item User and corporate account management modules.
            \item System configuration and monitoring tools.
            \item Fraud detection and alert systems.
        \end{itemize}
    \end{itemize}
\end{itemize}