\section{Functional Requirements}

Functional requirements describe the set of services and interactions that the system must provide to satisfy the users of Credix. They are organized according to the sprint-based development approach, covering core payment functionality, credit management capabilities, analytics and reporting features, and system administration.

\subsection{Core Payment Processing}
\begin{itemize}
    \item Generation of unique, time-bound (e.g., 30-second expiry) 1D barcodes (e.g., Code128 format) linked to the End-User's tokenized wallet ID.
    \item Real-time validation of barcode payments by the Spring Boot backend upon scanning by ASM POS terminals.
    \item Processing of payment transactions, including debiting the End-User's wallet and crediting the Vendor's account.
    \item Implementation of fraud detection rules (e.g., >5 transactions/min from one user) to block suspicious payments.
    \item Requirement of SMS One-Time Password (OTP) for payments exceeding a predefined threshold (e.g., 200 TND).
    \item Display of current digital wallet balance for End-Users with real-time updates.
\end{itemize}

\subsection{Credit Management (Sprint 3)}
\begin{itemize}
    \item \textbf{Bulk Credit Purchase}: Corporate clients can purchase credit in bulk through secure payment gateways with admin approval workflow.
    \item \textbf{Credit Distribution}: Allocation and de-allocation of credit to individual employees by Corporate clients with customizable spending limits.
    \item \textbf{Transaction Monitoring}: Real-time tracking of employee transactions, credit consumption, and remaining balances.
    \item Management of corporate credit pools, including top-up functionalities and expiry settings.
    \item Enforcement of corporate-defined spending policies (monthly limits, daily limits, vendor restrictions).
    \item Email notifications for credit allocation, depletion alerts, and policy violations.
\end{itemize}

\subsection{Analytics and Reporting (Sprint 4)}
\begin{itemize}
    \item \textbf{Spending Analytics}: Interactive dashboards displaying credit consumption trends, employee spending patterns, and vendor analysis.
    \item \textbf{Financial Reports}: Generation of comprehensive financial reports (credit allocation, usage summaries, transaction details) in PDF/CSV formats.
    \item Graphical visualization of key metrics with dynamic filtering capabilities (period, user, vendor, transaction type).
    \item Real-time analytics updates with drill-down capabilities for detailed transaction analysis.
    \item Automated report scheduling and delivery to corporate stakeholders.
    \item Comparative analytics across different time periods and employee groups.
\end{itemize}

\subsection{User and Account Management}
\begin{itemize}
    \item Creation, modification, and logical deletion of accounts (End-User, Vendor, Corporate, Administrator).
    \item Secure authentication (email/password, JWT, token refresh, biometric authentication for End-Users).
    \item Management of roles and permissions according to user type.
    \item Corporate account creation, modification, and management.
    \item Employee account management within corporate structures (addition, removal, status tracking).
\end{itemize}

\subsection{System Administration and Security}
\begin{itemize}
    \item Administrator dashboard for real-time system monitoring, fraud alerts, and user activity logs.
    \item System alerts for fraud attempts, system errors, or critical events.
    \item Secure tokenization of wallet IDs and sensitive data encryption.
    \item Multi-language support for notifications and interfaces (English, French, Arabic).
    \item Vendor dashboard displaying daily transaction summaries, settlement status, and payment history.
    \item Push notifications for all user types with customizable alert preferences.
\end{itemize}
